Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-11 paper.tex
update background

Robot interacting with humans, bla bla bla

@@

\section{Background}
\subsection{Reinforcement Learning}
\subsection{Human enhanced Reinforcement Learning}
One of the main challenge when applying RL to robotics is poor perfermance in
 the early stages of the learning as the agent has to explore the environment to
 gather initial knowledge. This challenge is especially
important for robotics as trials often have to happen in the real world (as
simulator close enough to the real world as not available) and as such can
present risks for the robot or for the persons interacting with it.

@@

\begin{algorithm}
    \DontPrintSemicolon
    \SetKwInOut{Input}{inputs}\SetKwInOut{Output}{output}
    \Input{Current state s, action-partial state rewards tuples}
    \Output{selected action $\pi(s)$}
    \ForEach{a $\in $ A}{
        \ForEach{ s'-r $\in C_{a}$}{
            compute similarity
            $\Delta(s',s)=1-\frac{\sum_{j}^{n'}(s'(j)-s(j))^{2}}{n'}$
        }
        $\Delta(a)=max(\Delta)$

@@

%===============================================================================
\section{Results}

>>>>

Human-Robot Interaction (HRI) aims at having humans and robot living together
in the society, interacting socially in many different environments and
contexts. Robot are expected to behave appropriately regardless of the domain
of interaction. However, not all behaviours are known in advance and can be
implemented in the robot before its deployment in the real world. Robots need
to be able to learn new tasks, new actions policies, new social norms and how
to make sense of the world surrounding them.

When interacting in the real world, humans face huge spaces of almost unlimited
dimensions, and despite this complexity, adults and even more children are able
to learn quickly, often from only a few demonstrations or examples. Humans are
able to take the most out of every datapoint availble to them. On the other
hand, recent advances in Machine Learning such as Deep Learning \cite{lecun2015deep}
have been made possible by the availability of huge dataset covering millions
of labeled examples or dozens of hours recording. These progress have
targetting either perception, where labeled datapoints can be available or
action selection in virtual environments where the impact of actions is
limited.

Similarly to humans, robots interacting in the real world will have to be able
to learn quickly, from different types of inputs: demonstrations, commands,
rewards and also autonomously.

@@

\section{Background}
\subsection{Reinforcement Learning}

The main framework to provide a robot with autonomous learning is Reinforcement
Learning (RL)(\cite{kober2013reinforcement,sutton1998reinforcement}. The main idea
behind reinforcement learning is that a agent is interacting in an environment
providing positive or numerical reward in reaction to the agent's actions and
the agent selects actions to maximise the expected cummulative discounted
reward.

Classic approaches RL relies on exploring virtual environments where the agent
tries to maximise the reward, but where in the end exploration often do not
have a real impact and where the agent can interact as long as needed to gather
enough information on the environment to find a correct action policy.

But in many real worl problem, relying only on random exploration to obtain
knowledge on the environment is not enough, the agent needs to have some initial
knowledge or additional knowledge provided often by humans to  work more
efficiently and achieve more complex results.

\subsection{Human enhanced Reinforcement Learning}
\subsubsection{Initial knowledge}
One way to use human knowledge to help an agent to learn is through providing
initial knowledge. 
alphago

IRL

OpenAI deep RL

One of the main challenge when applying RL to robotics is poor perfermance in
the early stages of the learning as the agent has to explore the environment to
gather initial knowledge. This challenge is especially
important for robotics as trials often have to happen in the real world (as
simulator close enough to the real world as not available) and as such can
present risks for the robot or for the persons interacting with it.

\subsubsection{Guiding the learning}
scafolding 
shaping
guidance

@@

\begin{algorithm}
    \DontPrintSemicolon
    \SetKwInOut{Input}{inputs}\SetKwInOut{Output}{output}
    \Input{Current state s, action-partial state rewards tuples}
    \Output{selected action $\pi(s)$}
    \ForEach{a $\in$ A}{
        \ForEach{s'-r $\in C_{a}$}{
            compute similarity
            $\Delta(s',s)=1-\frac{\sum_{j}^{n'}(s'(j)-s(j))^{2}}{n'}$
        }
        $\Delta(a)=max(\Delta)$

@@

%===============================================================================
\section{Challenges}

The main challenge for using Interactive Machine Learning is to translate the
state-action space between the human view and the algorithm view. This is one
important reason why many researchers in IML focuse on limiting the human impact
to providing reward~\cite{knox2009interactively} or kinesthetic demonstrations
in the robot space~\cite{billard2008robot}. However as shown by Thomaz and Breazeal~\cite{thomaz2008teachable}, using more complex inputs from the supervisor, such
as guidance biasing the action selection can lead to a better performance in the
learning. But to able to use these higher level and more complex inputs from
humans, these actions have to be translated in inputs usable for the learning
algorithm and/or the action selection mechanism.

The more complex the inputs from the humans are the more additional information
can be transmitted to the learning, allowing the agent to learn more complex
behaviours faster.

Similarly, as shown by Senft and al. in \cite{senft2017supervised}, providing
more control to the supervisor about the robot actions can lead to keep the
agent in relevant states of the environment and as such speeding the learning
and making it safer for the robot and people interacting with it. However this
method is dependent of letting the human know what action the robot is about to
execute, which relies on the robot to express its intention in a human
understandable way. (ADDREF - see Serge?)

Another challenge is state representation, the state accessed by the learning
algorithm and the one accessed by the supervisor can be represented is highly
different space, covering different features, and if the robot aims to profit
from the human initial knowledge, it needs to have access to similar features in
the environment to the ones the human is using, and the human needs to be able
to transmit these features to the learning algorithm.
(the representation of the state is often engineered by the programmers of the
algorithm, and space features not considered in the initial design could
actually be important in the final one. Idea of Deep Learning, but not enough
datapoints.)

Needs a parallel to human learning from humans
